Aldebaran~b's temperate past uncovered in planet search data

### 2018-04-24 paper/aldebaran.tex
lenape acknowledgement
eora acknowledgement

The authors would like to acknowledge the Gadigal people of the Eora Nation on whose ancestral lands the University of Sydney is built.

>>>>

The authors would like to acknowledge the Gadigal people of the Eora Nation on whose ancestral lands the University of Sydney is built, and we pay our respects their knowledge, and their elders past and present. We also give blessings and thanks to the Lunaape people and Lunaape Nation for allowing us to do this work on their homeland at New York University.
